### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
edit until excl. Pre-optimization of Coating Procedure
correct misspellings

%\td{https://en.wikipedia.org/wiki/Thesis}
%\ds{what is it? What is it used for? How does it work? What different kinds are there? }
%\ds{what? how? why?}
This chapter can be broken down into three sections. 
The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs} absorber.
The next section concerns the description of materials and scientific methods used during the experminental part of this work. 
The third and last part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions, which are accelerated to the surface, mostly originate from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g. argon) in plasma phase are mainly used for bombardmnt because of their inert properties. 
Oxygen or nitrogen can be added to the plasme to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

>>>>

%\td{https://en.wikipedia.org/wiki/Thesis}
%\ds{what is it? What is it used for? How does it work? What different kinds are there? }
%\ds{what? how? why?}
This chapter can be broken down into three sections. 
The first section tries to shine light on the evolution of PV and give some background information on \gls{cigs} absorber.
The next section concerns the description of materials and scientific methods used during the experinental part of this work. 
The third and last part focuses on the algorithmic, statistical and analytical methods used to optimize and predict material properties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions, which are accelerated to the surface, mostly originate from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g. argon) in plasma phase are mainly used for bombardment because of their inert properties. 
Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

\todo{what were the used settings: leybold etc.}
%Prior to \gls{iv} measurements the samples were sputtered with aluminium through a mask to produce a multitude of equidistant contacts with a Leybold UNIVEX450C Sputter System.
%Directional current sputtering was used with argon as inert gas at \SI{0.005}{\milli\bar} and with a power of \SI{40}{\watt} for \SI{700}{\second}.

### 2024-08-11 doc/Thesis/chapter/021-theory-calculations.tex
correct misspellings

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
%What is \gls{ml}? 
Some might argue that \gls{ml} is just overglorified statistics, but that is not the case. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different.
%
Statistics and \gls{ml} are two closely related field and statistics influences \gls{ml} a lot, but \gls{ml} is not just statistics with repackages with a new hip buzzword. 
They differ in their methods, approachs and goals. 
%
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This reduction of inputs allows a statistician to better study how a change in input variables can directly affect a output variable\cite{gontcharov2019}.
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastics)\cite{haertler2014statistisch} is the subject of finding mathematical models to describe the data whereas (classical) statistics is the domain of representing the data. 
Nonetheless, statistics and maths is at the very basis of \gls{ml}.

@@

\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modeled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common methods include linear regression, kernel ridge regression and support vector regression.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{EMMA}
\subsection{Evolutionary Model-based Multiresponse Approach}
\Gls{emma} is an implementation of \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
are predicted with the help of \gls{mars}. 
The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} (Comprehensive R Archive Network) package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions). %, whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$). 
Advantages of \Gls{mars} are that it uses less parameters and it produces continuous models with continous derivatives.
%
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
%
Furthermore, \gls{mars} has the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
%
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Machine Learning and Statistics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Why introduce machine learning to this project? 
%I wanted to apply and delve into what I've been studying during my undergrad courses. 
%This seemed like the perfect oppurtunity. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Is machine learning just hyped statistics? No! 
		%{https://doi.org/10.1177\%2F1352458520978648}
		%{Machine and deep learning in MS research are just powerful statistics – No}
		%{https://towardsdatascience.com/no-machine-learning-is-not-just-glorified-statistics-26d3952234e3?gi=35376367cf98}
%What is \gls{ml}? 
Some might argue that \gls{ml} is just over glorified statistics, but that is not the case\cite{Healy2021Machine}. 
Although \gls{ml} uses several statistical methods, their goal and frame conditions are different.
%
Statistics and \gls{ml} are two closely related field and statistics influences \gls{ml} a lot, but \gls{ml} is not just statistics with repackages with a new hip buzzword. 
They differ in their methods, approaches and goals. 
%
%\td{The goal of machine learning is to ???}
%
\Gls{ml} tries to predict unseen data points accurately and statistics is a subfield of maths which tries to get insight into a given data. 
For example, in a statistical model, it is desirable to reduce the number of inputs. 
This reduction of inputs allows a statistician to better study how a change in input variables can directly affect an output variable\cite{gontcharov2019}.
%pic from \url{https://towardsdatascience.com/notes-on-artificial-intelligence-ai-machine-learning-ml-and-deep-learning-dl-for-56e51a2071c2}
More precisely, mathematical statistics (stochastics)\cite{haertler2014statistisch} is the subject of finding mathematical models to describe the data whereas (classical) statistics is the domain of representing the data. 
Nonetheless, statistics and maths is at the very basis of \gls{ml}.

@@

\Gls{nn} (one of the most popular architectures for big data\cite{Chiroma2019}) are loosely modelled after the brain\cite{bishop1994neural}.
Artificial neurons (also called nodes), which are arranged in layers, 
are connected to each of the neurons of previous and next layers
and the weights (parameters of intensity), with which the data is routed from one neuron to another, 
are optimised during training. 
%
Convolutional-layer \gls{nn} excel in picture recognition\cite{Lecun1995conv} and are useful in quantum mechanics too\cite{westermayr2020combining}.
Other common methods include linear regression, kernel ridge regression and support vector regression.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{EMMA}
\subsection{Evolutionary Model-based Multiresponse Approach}
\Gls{emma} is an implementation of \gls{pso} in the \texttt{R} programming language. 
Each time step the dependent variables for all possible input variable combinations %$\mathbf{x} = \{x_1,\cdots ,x_N\}$ 
are predicted with the help of \gls{mars}. 
The \gls{mars} \gls{rf} is then used to chose the next position for each particle.
\Gls{mars} is a regression method introduced by Friedman's 1991 paper 
"Multivariate Adaptive Regression Splines"\cite{friedman1991multivariate}. 
The \texttt{CRAN} (Comprehensive R Archive Network) package which implements \gls{mars} is called \texttt{earth} due to \gls{mars} being trade marked\cite{mars}.
%%% MARS 
\gls{mars} is an extension of multivariate linear regression.
Friedman presented \gls{mars} as an alternative to piecewise polynomials (splines) and local averaging methods (e.g. kernel functions). %, whose number of parameter quickly \td{exceeds the practical} for moderate dimensional problems ($n>5$). 
Advantages of \Gls{mars} are that it uses less parameters and it produces continuous models with continuous derivatives.
%
%to higher dimensions (n > 2) is straightforward in principle but difficult in practice. 
%"These difficulties are related to the so-called “curse-of-dimensionality”, a phrase coined by Bellman (1961) to express the fact that exponentially increasing numbers of points are needed to densely populate Euclidean spaces of increasing dimension."\cite{friedman1988fitting}
%
Furthermore, \gls{mars} has the ability to fit (possibly complex) interactions and non-linearities without losing interpretability. 
%
%- "The key ingredient that advances this approach to general settings is the ability to fit (possibly complex) interactions among the variables through the product terms that are permitted to enter the approximation (9), if required by the fit."\cite{friedman1988fitting}
%% MARS MODEL SELECTION
%- "The approximation is developed in a forward/backwards stepwise recursive manner in analogy with the recursive partitioning approach. "\cite{friedman1988fitting}
%

### 2024-08-11 doc/Thesis/chapter/023-linreg-krr-svm.tex
work on todos until chap3
correct misspellings

%
\textbf{Linear regression} is one of the simplest methods to predict data. 
It persuades by its computational simplicity and easy interpretation. 
%Let's take this equation
\begin{equation}
\mathbf{y} = \mathbf{X} \mathbf{k} +c 
\end{equation}
Where $\mathbf{y} \in \mathbb{R}^n$ ($n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}\in \mathbb{R}^{n\times d}$ ($d$ is the the number of independent variables) is a matrix of independent variables. 
The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} chargon).
A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
\begin{align}
L_1&= \sum_i |y_i - \hat y_i| \\%= \sum_i \sum_j |y_i - x_{i,j}\cdot k_i+c| \\
L_2&= \sum_i(y_i - \hat y_i)^2 %= \sum_i \sum_j (y_i - x_{i,j}\cdot k_i+c)^2
\end{align}
%

@@

%\textbf{Kernel Ridge Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\Gls{krr}} combines ridge regression with the kernel method. 
A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transformation for every data point, which lowers computational costs.
A kernel is some kind of similarity measure 
which fulfills the requirements of nonnegativity, symmetry and linearity\cite{rupp2015machine}.
%\enlargethispage{\baselineskip}
%\looseness=-1
The following equations show definitions for 
linear~(eq.~\ref{eq:lin-kernel}), 
polynomial (eq.~\ref{eq:pol-kernel}), 
sigmoidal (eq.~\ref{eq:sig-kernel}) and 
radial basis functionial kernel~(eq.~\ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
A requirement for using kernels is having a dot product in the loss function. 
This can be accomplished by expressing $\mathbf{k}$ in terms of $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
\cite{rudin2020least}.

@@

Classifiction works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 

@@

The decision boundary can be expressed as an hyperplane

@@

By incorporation the contraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 

@@

which can be rewritten by some \td{mathematical wizardry} (setting the partial derivatives of the Lagrangian function

@@

Such data can be handeled by introducing a penalization term for wrongly categorized samples into the loss function. 

@@

The substraction of a negative number will result in a positive penalization. 

@@

the substraction will lead to a negative number and the maximum will be 0 if the sample is ousite of the margin. 

@@

Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the innerproduct of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper. 
%\td{write about sv regrgession}

>>>>

%
\textbf{Linear regression} is one of the simplest methods to predict data. 
It persuades by its computational simplicity and easy interpretation. 
%Let's take this equation
\begin{equation}
\mathbf{y} = \mathbf{X} \mathbf{k} +c 
\end{equation}
Where $\mathbf{y} \in \mathbb{R}^n$ ($n$ is the number of data points) is a vector of dependent variables which shall be predicted and $\mathbf{X}\in \mathbb{R}^{n\times d}$ ($d$ is the number of independent variables) is a matrix of independent variables. 
The parameters $\mathbf{k} \in \mathbb{R}^d$ and $c \in \mathbb{R}$ are chosen by minimizing an objective function (loss function in \gls{ml} jargon).
A typical function to minimize are the $L_1$ and $L_2$ error, i.e. \gls{mae} and \gls{mse}, respectively.
\begin{align}
L_1&= \sum_i |y_i - \hat y_i| \\%= \sum_i \sum_j |y_i - x_{i,j}\cdot k_i+c| \\
L_2&= \sum_i(y_i - \hat y_i)^2 %= \sum_i \sum_j (y_i - x_{i,j}\cdot k_i+c)^2
\end{align}
%

@@

%\textbf{Kernel Ridge Regression}
%%%%%%%%%%%%%%%%%%%%%%%%%%% { Kernel Ridge Regression } KRR %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{\Gls{krr}} combines ridge regression with the kernel method. 
A~kernel transforms data in such a way that a linear hyperplane (a point in one dimension, a line in two dimensions, 
a plane in three dimensions) can fit data in regression problems or separate the data in classification problems without actually doing the transformation for every data point, which lowers computational costs.
A kernel is some kind of similarity measure 
which fulfills the requirements of non-negativity, symmetry and linearity\cite{rupp2015machine}.
%\enlargethispage{\baselineskip}
%\looseness=-1
The following equations show definitions for 
linear~(eq.~\ref{eq:lin-kernel}), 
polynomial (eq.~\ref{eq:pol-kernel}), 
sigmoidal (eq.~\ref{eq:sig-kernel}) and 
radial basis functional kernel~(eq.~\ref{eq:rbf-kernel}), with $\gamma$ as fixed hyperparameter and $c_0$ as parameter to optimize.
A requirement for using kernels is having a dot product in the loss function. 
This can be accomplished by expressing $\mathbf{k}$ in terms of $\mathbf{X}$: $\mathbf{k}=\mathbf{X}^\top \mathbf{r}$
\cite{rudin2020least}.

@@

Classification works by spanning a hyperplane between two linearly separable categories in a way such that the closest points from each category have the largest distance to the hyperplane. 

@@

The decision boundary can be expressed as a hyperplane

@@

By incorporation the constraint (eq. \ref{eq:svm01}) via the Lagrangian multiplier method we 

@@

which can be rewritten by some mathematical 
%wizardry
acrobatics
(setting the partial derivatives of the Lagrangian function

@@

Such data can be handled by introducing a penalization term for wrongly categorized samples into the loss function. 

@@

The subtraction of a negative number will result in a positive penalization. 

@@

the substraction will lead to a negative number and the maximum will be 0 if the sample is outside of the margin. 

@@

Again, a kernel $K(\mathbf{x}_i, \mathbf{x}_j) = T(\mathbf{x}_i)^\top \cdot T(\mathbf{x}_j)$ allows to calculate the inner product of two vectors in a transformed space without the need of transforming each vector, which turns out to be computationally much cheaper. 
%\td{write about sv regrgession}
